### 2022-01-04 intro.tex
fixing intro

The number and applications of \acp{CPS}~\cite{Rajkumar2010CPS} --- that is, systems in which a real, physical mechanism is controlled by a computer --- have exploded in later years.
This rise in popularity is in great part driven by the advent of novel wireless communication technologies as well as networking paradigms, such as cellular 5G and Edge (and Fog) Computing.

In particular, \acp{NCS}~\cite{Gupta2010NCSOverview}, a type of \ac{CPS} wherein multiple networked actuators and sensors form a part of the same automatic control system, have been of great interest to the scientific community in the last decade.
Due to their potential advantages for industrial settings~\cite{Lu2015WSAN}, a large body of work exists dedicated to the modelling and performance characterization of these systems~\cite{Hespanha2007Survey,Zhang2013Survey,Zhang2016Survey}.
\Acp{NCS} enhance the flexibility of and improve existing control systems by allowing for the distribution of control functions over and across networks.
This allows for --- for instance --- simultaneous centralized coordination, control, and monitoring of potentially hundreds of devices.

@@

As evidence by the discussion above, experimental research in \acp{NCS} includes a large variety of heterogeneous hardware and software platforms, as well as methodologies and \acp{KPI}.
This, in turn, leads to hardware, software, and methodology fragmentation, as different studies tend to prefer approaches more favored in their respective communities.
Furthermore, existing studies tend to focus on individual aspects and components of a system, thus producing results which do not provide a complete image of the \ac{NCS}.
We identify thus a gap in knowledge pertaining to the reproducibility and comparison of experimental studies on these systems.

@@

In this paper, we present thus the first fully-software-based \ac{NCS} benchmarking framework with scalability and repeatability as its main focus.
This framework is built on top of the \emph{Python 3.8}~\cite{Python3.8} language, making it highly extensible and able to harness the tremendous amount of already existing user-provided libraries and packages~\cite{pypi}.
Additionally, it is fully compatible with \emph{containerization} technologies such as \emph{Docker}~\cite{merkel2014docker}, making it suitable for automated deployment and benchmarking on industry-standard setups using container orchestration technologies.
We name this framework \ac{CLEAVE}.

>>>>

The number and applications of \acp{CPS}~\cite{Rajkumar2010CPS} --- that is, systems in which a real, physical mechanism is controlled by a computer --- have exploded in later years.
However, this rapid increase in adoption of these systems has been mostly limited to industrial contexts.
Although \acp{CPS} present huge opportunities for all facets of society, they have yet to reach our daily lives in any relevant scale due to their stringent operational requirements.
This is about to change, however, as with the advent of novel wireless communication technologies as well as networking paradigms, such as cellular 5G and Edge (and Fog) Computing~\cite{Satya2009Case}, comsumer-grade \acp{CPS} will be made possible.
These technologies meet two key requirements of \acp{CPS}: real-time capabilities (through extremely low end-to-end latencies), and context- and locality-awareness, and will most likely become the backbone of \ac{CPS} in the future.

A subcategory of \acp{CPS} which stands to particularly benefit from the adoption of the above technologies is \acp{NCS}~\cite{Gupta2010NCSOverview}, a type of \ac{CPS} wherein multiple networked actuators and sensors form a part of the same automatic control system.
Depending on the physical system being controlled, \acp{NCS} can have extremely stringent timing and reliability requirements for the communication between plant and controller; requirements that conventional cloud computing and cellular networks are unable to meet~\cite{Liu2017Review,Wan2020Efficient}.

% These systems have been of great interest to the scientific community in the last decade.
Due to their potential advantages for industrial and commercial settings~\cite{Lu2015WSAN}, a large body of work exists dedicated to the modelling and performance characterization of \aclp{NCS}~\cite{Hespanha2007Survey,Zhang2013Survey,Zhang2016Survey}.
\Acp{NCS} enhance the flexibility of and improve existing control systems by allowing for the distribution of control functions over and across networks.
This allows for --- for instance --- simultaneous centralized coordination, control, and monitoring of potentially hundreds of devices.

@@

As evidenced by the discussion above, experimental research in \acp{NCS} includes a large variety of heterogeneous hardware and software platforms, as well as methodologies and \acp{KPI}.
This, in turn, leads to hardware, software, and methodology fragmentation, as different studies tend to prefer approaches more favored in their respective communities.
Furthermore, existing studies tend to focus on individual aspects and components of a system, thus producing results which do not provide a complete image of the \ac{NCS}.
We identify thus a gap in knowledge pertaining to the reproducibility and comparison of experimental studies on these systems.

@@

In this paper, we present thus the first fully-software-based \ac{NCS} benchmarking framework with scalability and repeatability as its main focus, built with the Edge in mind.
In the years since the advent of the Edge computing paradigm, more and more variations of it have appeared in literature as the paradigm starts to be adopted by industry.
``Near'', ``far'', ``core'', and ``telco'' edge, among others, are all terms which describe variations of the original concept and which are becoming ubiquitous in new research.
While the main idea of Edge computing is widely accepted as fundamental for pervasive \acp{NCS} in general, understanding the usefulness, strenghts, and weaknesses of such different edge concepts is becoming more and more important.

Our framework, which we name \ac{CLEAVE}, thus aims to simplify the repeatable and scalable benchmarking of such systems. 
It is built on top of the \emph{Python 3.8}~\cite{Python3.8} language, making it highly extensible and able to harness the hundreds-of-thousands of already existing user-provided libraries and packages~\cite{pypi}.
Additionally, it is fully compatible with \emph{containerization} technologies such as \emph{Docker}~\cite{merkel2014docker}, making it suitable for automated deployment and benchmarking on industry-standard cloud and (more importantly) edge setups using container orchestration technologies.
